Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2018-03-29 paper/ms.tex
Added Rough Outline

\shorttitle{Short Paper Title}

@@

\title{Paper Title}

\author{
Some Awesome People\altaffilmark{1,2,3,4}
}

\altaffiltext{1}{
  Department of Physics and Astronomy,
  Stony Brook University, Stony Brook, NY, 11794-3800, USA; \\
  \href{mailto:somebody@someplace}{somebody@someplace}
}
\altaffiltext{2}{
  Department of Physics and Astronomy,
  The University of Alabama, Tuscaloosa, AL, 35487-0324, USA
}
\altaffiltext{3}{
  Department of Physics and Astronomy,
  Stony Brook University, Stony Brook, NY, 11794-3800, USA
}
\altaffiltext{4}{
  Institute for Advanced Computational Sciences,
  Stony Brook University, Stony Brook, NY, 11794-5250, USA
}

\begin{abstract}
Awesome Abstract
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}

Introduction with a pretty plot in \figref{fig:progenitor_abundances}.

\begin{figure}[t]
	\includegraphics[width=\linewidth]{figures/samples/cf_wdb_mesa_comp_vs_mass.pdf}
	\caption{\label{fig:progenitor_abundances} Abundance profile
          of \MESA\ progenitor (\MESA) and its reconstruction on a
          uniform grid at $4$~km spatial resolution with the hydrostatic equilibrium condition of
          \eqqref{eq:hse_pressure} enforced (\FLASH). The reduced set
          of nuclides are shown, where $\mathrm{X_{\Ox{16}} = 1 -
            X_{\C{12}} - X_{\Ne{20}} - X_{\Ne{22}}}$ for the
          abundances labeled \FLASH. Solid lines and circles denote
          the abundances used in \FLASH\ whereas plain solid lines
          denote the abundances used in \MESA.}
\end{figure}

\section{Methodology}

Methodology goes here.

A handy example of a vertical multi-plot figure is \figref{fig:znd_abundances}.

\begin{figure}[t]
	\begin{minipage}{0.5\textwidth}
		\includegraphics[width=0.86\textwidth]{figures/samples/XvsT_wn_0_XC-50.pdf}
		%\caption{\label{fig:znd_abundances_xc12_0.5} Initial composition: $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.50$, $X_{^{20}Ne} = 0.00$}
	\end{minipage}	
	\hfill
	\begin{minipage}{0.5\textwidth}
		\includegraphics[width=0.86\textwidth]{figures/samples/XvsT_wn_20_XC-30.pdf}
		%\caption{\label{fig:znd_abundances_xc12_0.3} Initial composition: $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.30$, $X_{^{20}Ne} = 0.20$}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\textwidth}
		\includegraphics[width=0.86\textwidth]{figures/samples/XvsT_wn_35_XC-15.pdf}
		%\caption{\label{fig:znd_abundances_xc12_0.15} Initial composition: $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.15$, $X_{^{20}Ne} = 0.35$}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\textwidth}
		\includegraphics[width=0.86\textwidth]{figures/samples/XvsT_wn_45_XC-05.pdf}
		%\caption{\label{fig:znd_abundances_xc12_0.05} Initial composition: $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.05$, $X_{^{20}Ne} = 0.45$}
	\end{minipage}
        \caption{\label{fig:znd_abundances} Mass Fraction Evolution for ZND Detonations with varying initial \C{12} and \Ne{20} mass fractions, calculated for an initial density of $10^7~\grampercc$.}
\end{figure}

Here's a text citation \citet{timmes92,Chametal08}, and here's a parenthetical citation ~\citep{timmes.swesty:accuracy,castro1}.

Here's an ordinary equation in \eqref{eq:hse_pressure}.

\begin{equation}\label{eq:hse_pressure}
  P_{EOS}(\rho_i,T_i,X_i) = \frac{g \Delta r}{2} (\rho_i +
  \rho_{i-1})\ .
\end{equation}

Here's a multi-line equation.

@@

\section{Simulations and Results}

Simulations and results go here.

Example of multi-figure plot that spans the columns is given by \figref{fig:cone_delayed_core}.

>>>>

\shorttitle{Hybrid Ia Progenitors}

@@

\title{Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors}

\author{
Carlyn N.\ Augustine\altaffilmark{1},
Donald E.\ Willcox\altaffilmark{2},
Dean M.\ Townsley\altaffilmark{3},
and Alan C.\ Calder\altaffilmark{2,4}
}

\altaffiltext{1}{
  Department of Physics and Astronomy,
  The University of Alabama, Tuscaloosa, AL, 35487-0324, USA
}
\altaffiltext{2}{
  Department of Physics and Astronomy,
  Stony Brook University, Stony Brook, NY, 11794-3800, USA; \\
  \href{mailto:donald.willcox@stonybrook.edu}{donald.willcox@stonybrook.edu}
}
\altaffiltext{3}{
  Institute for Advanced Computational Sciences,
  Stony Brook University, Stony Brook, NY, 11794-5250, USA
}

\begin{abstract}
We present simulations of thermonuclear (type Ia) supernovae
from hybrid C/O/Ne progenitor white dwarfs. These progenitors 
were evolved though accretion with the \MESA\ stellar evolution code 
and include blah blah about the new hybridocity....
For comparison, we performed a set of supernova simulations from
traditional C/O progenitors....
We find ....
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
Type Ia supernovae (\SNeIa) are bright stellar explosions....

Phillips relation
~\citep{phillips:absolute}.

Cosmology
due to dark energy \citep{riess.filippenko.ea:observational,
perlmutter.aldering.ea:measurements,leibundgut2001}.

Brief discussion of progentors...
ancient history~\citep{hoylefowler60,arnett.truran.ea:nucleosynthesis}. The
Single degenerate 
\citep{hoylefowler60,trucam71,whelaniben73,Nomo84}. Alternately, in

Other models
\citep{webbink84,ibentutukov84}, in which two WDs inspiral and merge.

Hybrid models 
old 
\citep{denissenkovetal2015}
\citet{Wangetal2014} and \citet{Mengetal2014} presented binary

Recent results from stellar evolution
The models we are exploding \citep{brooksetal2017}

If we refer to the work by name, it should appear ``The hybrid models
of~\citet{brooksetal2017}." Or, we can just cite it~\citep{brooksetal2017}.

Here's the other Books paper \citep{brookset2017}. Do we need to mention it?
Give a read to see!

\subsection{The Chandrasekhar-mass Single Degenerate Scenario}

Explain the Single Degenerate scenario
\citep{Baraffe2004Stability-of-Su,WoosWunsKuhl04,wunschwoosley2004,Kuhletal06,nonakaetal2012}.
expansion \citep{Nomo84,WoosWunsKuhl04}, and a flame is born.

Explain DDT

Go through below and cite some of these as you tell the story

d~\citep{arnett.truran.ea:nucleosynthesis}.
~\citep{mazzalietal2008}.

\citep{khokhlov1993,bychovliberman1995,
SNrt,Khok95,NiemHill95,khoketal1997,ZingDurs07,
cholazarianvishniac2003,
roepkehn2003,roepkehn2004,
Zingale2005Three-dimension,Schmetal06a, Schmetal06b,Aspdetal08,
Woosetal09,csetal2009,hicksrosner2013,c-ssr2013,
jacketal2014,poludnenko2015,hicks2015}.

A deflagration alone will not produce a event of normal brightness and
expansion velocity~\citep{roepkeetal07}. Instead, the initial
deflagration must transition to a detonation after the star has
expanded some in order to produce abundances and a stratified ejecta
in keeping with
observations~\citep{Khokhlov1991Delayed-detonat,hokowh95}.
The physics of this ``deflagration-to-detonation transition'' (DDT)
are not completely understood, but there has been considerable study
based on mechanisms involving flame fronts in highly turbulent
conditions~\citep{1986SvAL, woosley90, Khokhlov1991Delayed-detonat,
  hokowh95, HoefKhok96, khoketal1997, NiemWoos97, hwt98, Niem99,
  GameKhokOran05,roepke07, poletal2011,c-ssr2013,poludnenko2015}.
These models generally reproduce the observations under certain
assumptions about the ignition~\citep{townetal2009}, but research has
shown that the results are very sensitive to the details of the
ignition~\citep{PlewCaldLamb04,GameKhokOran05,garciasenz:2005,
  roepkeetal07,Jordan2008Three-Dimension}.

Summarize what we do a la:
In our simulations, we initialize a detonation once the 
deflagration front reaches a
characteristic DDT fuel density, which controls the degree of
expansion the star undergoes during the deflagration stage.

The comparison study of tradition C/O progentor WDs used the same
initial conditions for the realizations within the suite. Make the
point that the traditional models are simalted with the same code
and the same set if perturbations on the initial match head (that is
what we mean by a realization). The only difference is the different
nuclear buring to include the other Ne and the initial profile of
the 1-d model.

For much of the methodology to be described below, just say a few
words about what was done and cite \citet{willcoxetal2016}.

\section{Methods}
\section{Inital Models}
\section{Results}
\section{Discussion and Conclusion}
\section{Below here from Dons paper}
\subsection{Systematic Effects}

Contemporary observational campaigns typically investigate how
the brightness and rates of supernovae correlate to 
properties of the host galaxy such as mass and star formation
rate~\citep[c.f.][]{graurmaoz2013,graurbiancomodjaz2015}. Of
particular interest is the delay time distribution (DTD), the
supernovae rate as a function of time elapsed from 
early, rapid
star formation in the host galaxy, and how it may be used
to constrain progenitor models~\citep{hachisu:2008,
conleyetal2011,howell2011,grauretal2011,biancoetal2011,maozmannuccibrandt2012}.
See also the review by~\citet{maozmannucci2012}.
Very recent results indicate evolution of the UV spectrum with 
redshift, providing evidence for systematic effects with
cosmological time \citep{milneandfoley2015}.

Motivated by this interest in correlations between properties of the
host galaxy and the brightness and rate of events, earlier incarnations of  
our group performed suites of simulations in the DDT scenario
with a modified version the \FLASH\ code (described below) to explore
systematic effects on the brightness of an event measured by the yield of
$^{56}$Ni~\citep{Krueger2010On-Variations-o,jacketal2010,kruegetal12}. The
study we present here explores how explosions following from a new class
of ``hybrid" 
progenitors~\citep{denissenkovetal2013,chenetal2014,denissenkovetal2015} 
compares to these previous results.

\section{Hybrid Progenitor Models}\label{section:hybrid_progenitor_models}
Rumors that the structure and evolution of stars is a solved
problem~\citep{HansenEtAl04} are greatly exaggerated. Recent
developments obtained with the modern software instrument
\MESA~\citep{mesa1,mesa2,mesa3,mesa3e} indicate that convective boundary
mixing (CBM) in the cores of super asymptotic giant branch stars
(super-AGB) plays a more critical role than previously thought.  There
are several examples in which the inclusion of CBM improves agreement
between models and observations, including that
of~\citet{denissenkovetal2013}, which studied WD interior shell
convection, and~\citet{herwig2005, werner.herwig.2006}, which treated
He-shell burning in AGB stars.
\citet{denissenkovetal2013,chenetal2014} found that in some super-AGB
stars, CBM halts the progression of carbon burning into the stellar
core, leaving an unburned C-rich core as large as $0.2~\Msun$
surrounded by an O-Ne-rich intershell region extending out to the
accretion layer at the end of hydrostatic carbon burning. This effect
of C-flame quenching via CBM is also confirmed by the extensive
parameter study on C-burning in super-AGB stars
in~\citet{farmeretal2015}. Nevertheless, the true test of
  whether or not CBM is effective enough to quench the carbon flame
  awaits sufficiently resolved hydrodynamic simulations or further
  evidence via observational consequences.

Accounting for CBM, ~\citet{denissenkovetal2015} explored
the stellar evolution of a super-AGB star with initial mass of
$6.9~\Msun$ and obtained the hybrid white dwarf that is the focus of
the present work. After hydrostatic carbon burning has ceased, the
white dwarf accretes carbon-rich material at its surface, leading to
the rise of temperature near its center. This results in carbon
burning in the upper layer of the small carbon-rich core, which,
together with the thermal effects of the $\Ne{23}/\Na{23}$ Urca process,
provides off-center heating~\citep{denissenkovetal2015} that drives
convection throughout the entire white dwarf except the carbon-rich
core.

Convection subsequently mixes the carbon-poor material in the
O-Ne intershell region with carbon-rich material on the accreted layer
and also partially mixes carbon-rich material from the core with the
carbon-poor material in the O-Ne intershell. This proceeds along with
accretion and carbon burning, until the latter yields peak
temperatures near $10^9$~\K, around which the local heating time is
shorter than the eddy turnover time so as to ignite thermonuclear
runaway~\citep{wunschwoosley2004}. At this point, the carbon-rich core
has been significantly depleted of carbon and consists mostly of
\Ox{16} and \Ne{20}, while the O-Ne intershell region has been
enriched to a \C{12} abundance of $\approx 0.14$ due to convective
mixing. This scenario, immediately preceding the \SNIa-like explosion,
is shown in \figref{fig:progenitor_abundances} and
\figref{fig:progenitor_temperatures}.  The process of mapping this
\MESA\ progenitor into hydrostatic equilibrium in \FLASH\ is described
in~\secref{subsec:mesa_flash_mapping}.

This hybrid WD has the interesting property that its mass before the
onset of accretion is $1.06~\Msun$, naturally closer to the
Chandrasekhar limit than a traditional C-O WD. Such
hybrid WD progenitors thus require less mass accretion to approach
the Chandrasekhar limit, which helps to resolve one of the
difficulties with the SD progenitor
system~\citep{denissenkovetal2015,chenetal2014,kromeretal2015}. The
mass of this hybrid WD following accretion is $1.36~\Msun$.

We note that these models include the influence of the URCA process on the 
convective phase of the pre-explosion progenitor. Our progenitor profiles are
taken directly from \MESA\ models presented in ~\citet{denissenkovetal2015}. 
These include contributions to the energy from thermal energy produced
by the URCA process, but the underlying mixing length theory was not 
modified correspondingly. Thus the effect on the convection is only
due to the energy loss/generation rate. Our progenitor profiles are
shown in Figures \ref{fig:progenitor_abundances} and \ref{fig:progenitor_temperatures}
and correspond to the models in Figure 9a of~\citet{denissenkovetal2015}.
In this regard, this progenitor differs from the carbon-core
models of~\citet{kromeretal2015} in that it includes the pre-explosion convective
burning phase that spreads the carbon enrichment throughout the star before
ignition of the flame front.
% They also differ in that they are a DDT
% Also discuss Marquadt 2015.
While the progenitor we study consists mostly of \Ox{16}
  and \Ne{20}, having the average composition of (\C{12} = 0.17,
  \Ox{16} = 0.42, \Ne{20} = 0.32), it differs from the O-Ne white
  dwarf of~\citet{marquardtetal2015} by having a much higher abundance
  of \C{12} due to accumulation and mixing of \C{12} material during
  the accretion phase, as described above. As discussed below in
  \secref{subsec:one_burning_mods} and
  \secref{subsec:hybrid_ignition_parameters}, given the temperature
  profile of \figref{fig:progenitor_temperatures}, this available
  \C{12} is sufficient to drive both a subsonic deflagration and
  subsequently a supersonic detonation front as in previous work that
  applied the same DDT approach to C-O white dwarf
  progenitors~\citep{kruegetal12}.

\begin{figure}[t]
	\includegraphics[width=\linewidth]{figures/progenitor_400k/Dr-400k/cf_wdb_mesa_comp_vs_mass.pdf}
	\caption{\label{fig:progenitor_abundances} Abundance profile
          of \MESA\ progenitor (\MESA) and its reconstruction on a
          uniform grid at $4$~km spatial resolution with the hydrostatic equilibrium condition of
          \eqqref{eq:hse_pressure} enforced (\FLASH). The reduced set
          of nuclides are shown, where $\mathrm{X_{\Ox{16}} = 1 -
            X_{\C{12}} - X_{\Ne{20}} - X_{\Ne{22}}}$ for the
          abundances labeled \FLASH. Solid lines and circles denote
          the abundances used in \FLASH\ whereas plain solid lines
          denote the abundances used in \MESA.}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=0.9\linewidth]{figures/progenitor_400k/Dr-400k/cf_wdb_mesa_temp.pdf}
	\caption{\label{fig:progenitor_temperatures} Temperature
          profile of \MESA\ progenitor (\MESA) shown with a solid red
          line and its reconstruction on a uniform grid at $4$~km spatial resolution (\FLASH) with
          grid zones shown in blue circles.}
\end{figure}

\section{Methodology}
A few significant new developments in our computational methods were
necessary to simulate the explosion of the hybrid C-O-Ne WD. In
\secref{subsec:one_burning_mods}, we obtain the steady-state
detonation structure for the hybrid C-O-Ne fuel and compare its
detonation characteristics with those of C-O fuel to analyze the
suitability of our combustion model in \FLASH. Then in
\secref{subsec:mesa_flash_mapping} we map the hybrid C-O-Ne WD into a
uniform spatial grid to initialize \FLASH\ while taking care to
preserve hydrostatic equilibrium. We comment in
\secref{subsec:flash_flame} on our \FLASH\ combustion model and in
\secref{subsec:ddt_details} on the deflagration to detonation
transition (DDT) scheme. Finally, we describe the simulation geometry
and the adaptive mesh refinement used in
\secref{subsec:flash_geometry}.

\subsection{Modifications for C-O-Ne Burning} 
\label{subsec:one_burning_mods}

The combustion model in \FLASH\ that we use for Type Ia supernovae
simulations \citep{Caldetal07, townsley.calder.ea:flame,
  SeitTownetal09, townetal2009, jacketal2014, townetal15} separates
the burning into four states: unburned fuel, C-fusion ash, a
silicon-group-dominated nuclear statistical quasi-equilibrium (NSQE)
state, and a full nuclear statistical equilibrium (NSE) state
dominated by iron-group elements (IGEs). The progress of combustion
from one of these states to the next is tracked by three scalar
progress variables whose dynamics is calibrated to reproduce the
timescales of reactions that convert material among these
states. Previous work has focused on fuel mixtures composed
principally of $^{12}$C, $^{16}$O, and $^{22}$Ne.  Simulation of the
hybrid models required extension of this burning model to account for
the presence of \Ne{20} as a large abundance in the fuel. Here we
describe both how $^{20}$Ne is processed during combustion, and the
modifications made to the burning model that accommodate it.

The burning stages above are determined by the hierarchy of timescales
for the consecutive consumption of C and O via fusion and Si via
photo-disintegration and alpha capture. Investigation of the inclusion
of \Ne{20} focused on whether an additional Ne-consumption stage would
be required, and, if not, what stage should include Ne consumption. In
order to characterize the physical burning sequence that we want to
model, we performed a series of simulations of detonations propagating
through WD material with the TORCH nuclear reaction network
software~\citep{timmes1999,torch}.\footnote{TORCH is available from
  \url{http://cococubed.asu.edu}, and the modified version used for
  this study is available from
  \url{http://astronomy.ua.edu/townsley/code}.} TORCH is a general
reaction network package capable of solving networks with up to
thousands of nuclides. A mode is implemented that computes the
one-dimensional spatial thermodynamic and composition structure of a
steady-state planar detonation using the the Zel'dovich, von Neumann,
and D\"{o}ring (ZND) model \citep{FickDavi79,townetal15}. We use a
reaction network composed of 225 nuclides consisting of the 200
nuclides in \citet{Woosley1995The-Evolution-a} in addition to the 25
neutron-rich nuclides added by \citet{Caldetal07} to improve coverage
of electron capture processes in the Fe group.

For the multi-species fuel and ash relevant to typical white dwarf material, the ZND detonation exhibits the stages that motivate the combustion model.
Figure \ref{fig:co_znd_stages} shows these stages as they appear in a
ZND detonation calculation in fuel with the fractional composition
(\C{12} = 0.50, \Ox{16} = 0.48, \Ne{22} = 0.02) corresponding to
the composition found in the interior of a C-O WD, and a fuel density of $10^7$~g~cm$^{-3}$.
The evolution of the mass fractions in time following the passage of the shock through 
the zone of material is plotted below the density structure in Figure \ref{fig:co_znd_stages}.
The time range of the four states representing the burning stages are indicated by colors in the upper panel of Figure \ref{fig:co_znd_stages}, with the consecutive states separated by the
\C{12}-\Si{28}, \Ox{16}-\Si{28}, and \Si{28}-\Fe{54} crossing times.
It can be seen that the times of the density plateaus are directly comparable to the times at which the primary energy release transitions from one fuel source to another, 
as, e.g., when the \C{12} fraction has fallen
to $\approx1\%$ of its initial value just before $10^{-8}$~s.

\begin{figure}[t]
  \includegraphics[width=\linewidth]{figures/detonation_plotfiles/Composition_Density_vs_Time.pdf}
	\caption{\label{fig:co_znd_stages} Density (upper) and
          abundance (lower) structure in the post-shock flow of a ZND
          detonation calculation of C-O WD material. The upper panel is shaded to show
          the fuel (red), ash (blue), NSQE (green), and NSE (gray) burning stages, demarcated by the \C{12}-\Si{28}, \Ox{16}-\Si{28}, and
          \Si{28}-\Fe{54} crossing times. The initial composition is
          $X_{^{16}\rm O} = 0.48$, $X_{^{22}\rm Ne} = 0.02$,
          $X_{^{12}\rm C} = 0.50$, and $X_{^{20}\rm Ne} = 0.00$, and
          the pre-shock density is $10^7$~g~cm$^{-3}$.}
\end{figure}

In our combustion models for C-O progenitors, consumption of the
initial fuel is modeled as a two-step process. The two stages
represent the consumption first of \C{12}, then of \Ox{16}, mimicking
the sequence seen in the detonation structure shown in
Figure~\ref{fig:co_znd_stages} for ``Fuel'' and ``Ash'' stages. At the
end of this second stage the material is in a \Si{28}-dominated NSQE
state~\citep{Caldetal07,townsley.calder.ea:flame}. To determine how
the burning stages change with the inclusion of \Ne{20}, as is the
case in the hybrid C-O-Ne progenitor, we perform ZND calculations with
an admixture of \Ne{20} ranging from $0.01$ to $0.45$, at the expense
of \C{12} content. For each composition we find the minimally
overdriven solution, as was done in the C-O case. Out to the minimum
in density, this solution is the same as the eigenvalue ZND solution,
which corresponds to a self-supported detonation \citep{FickDavi79,townetal15}.
This computation gives the resolved detonation structure in C-O-Ne Hybrid WD matter.

\begin{figure}
	\includegraphics[width=\linewidth]{figures/detonation_plotfiles/Vdet_vs_xc12_w_fit_includebump.pdf}
	\caption{\label{fig:detonation_velocity_wfit} Self-supported detonation speed plotted versus carbon fraction in fuel with initial (pre-shock) density of $10^7$~\grampercc and initial composition of $X_{^{16}\rm O} = 0.48$ and $X_{^{22}\rm Ne} = 0.02$. The sum $X_{^{12}\rm C} + X_{^{20}\rm Ne}$ is kept constant.\\}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=0.95\linewidth]{figures/detonation_plotfiles/dens_multi_new.pdf}
        \caption{\label{fig:co_znd_multi_den}} Density structures shaded with varying $^{12}$C mass fraction, keeping constant the sum $X_{^{12}\rm C} + X_{^{20}\rm Ne}$. The rest of the composition is $X_{^{16}\rm O} = 0.48$ and $X_{^{22}\rm Ne} = 0.02$.
\end{figure}

The eigenvalue detonation speeds from ZND calculations in material with \C{12} fraction varying from 0.05 to 0.5 are shown in Figure \ref{fig:detonation_velocity_wfit}, demonstrating that self-supported detonations in this progenitor are feasible with only small variation in speed across this range of \C{12} fractions. 
Figure \ref{fig:co_znd_multi_den} shows
the effect of simultaneously adding \Ne{20} and reducing \C{12} on the density profile.
Lowering the \C{12} fraction weakens the shock and
lengthens the timescales of the step features, corresponding to more slowly
burning fuel and ash, as might be expected from the lower energy release
afforded by the \Ne{20}. However, it is noteworthy that no qualitatively
new features arise from the change in fuel source that would suggest
that more than 4 representative burning stages are needed.

\begin{figure}[t]
	\begin{minipage}{0.5\textwidth}
		\includegraphics[width=0.86\textwidth]{figures/detonation_plotfiles/XvsT_wn_0_XC-50.pdf}
		%\caption{\label{fig:znd_abundances_xc12_0.5} Initial composition: $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.50$, $X_{^{20}Ne} = 0.00$}
	\end{minipage}	
	\hfill
	\begin{minipage}{0.5\textwidth}
		\includegraphics[width=0.86\textwidth]{figures/detonation_plotfiles/XvsT_wn_20_XC-30.pdf}
		%\caption{\label{fig:znd_abundances_xc12_0.3} Initial composition: $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.30$, $X_{^{20}Ne} = 0.20$}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\textwidth}
		\includegraphics[width=0.86\textwidth]{figures/detonation_plotfiles/XvsT_wn_35_XC-15.pdf}
		%\caption{\label{fig:znd_abundances_xc12_0.15} Initial composition: $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.15$, $X_{^{20}Ne} = 0.35$}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\textwidth}
		\includegraphics[width=0.86\textwidth]{figures/detonation_plotfiles/XvsT_wn_45_XC-05.pdf}
		%\caption{\label{fig:znd_abundances_xc12_0.05} Initial composition: $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.05$, $X_{^{20}Ne} = 0.45$}
	\end{minipage}
        \caption{\label{fig:znd_abundances} Mass Fraction Evolution for ZND Detonations with varying initial \C{12} and \Ne{20} mass fractions, calculated for an initial density of $10^7~\grampercc$.}

\end{figure}

Qualitative similarity between C-O and C-O-Ne detonation structures
are visible in the mass fractions as well.
To demonstrate this, the abundance structures with initial \C{12} abundances of 0.5, 0.3,
0.15, and 0.05 are shown in \figref{fig:znd_abundances}. 
We find that the \Ne{20} burns simultaneously with whatever \C{12} is present,
producing primarily \Si{28}.  The Ne-C burning stage is then followed by \Ox{16}
burning to silicon-group NSQE elements and then on to NSE,
just as in a model with no initial \Ne{20}, except for the progressively
later \Ox{16} burning time.

\begin{figure}[t]
	\includegraphics[width=1\linewidth]{figures/detonation_plotfiles/nuclides_xmax_xc12_15.pdf}
	\caption{\label{fig:nuclides_xmax} Our reaction network of 225 nuclides is shown, with nuclides shaded by their maximum abundance and categorized based on whether they were maximally abundant before the earliest of the following crossing times: \C{12}-\Si{28} (purple), \Ox{16}-\Si{28} (blue), \Si{28}-\Fe{54} (green). Nuclides maximally abundant after the \Si{28}-\Fe{54} crossing time are shown in orange.
		The initial composition used 
		is $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.15$, and $X_{^{20}Ne} = 0.35$.
	}
\end{figure}

A graphic representation of the most significant nuclides by mass
fraction and the stage in which they are important is shown in
\figref{fig:nuclides_xmax} for an initial \C{12} fraction of 0.15,
representative of the majority of the hybrid stellar profile
(cf. \figref{fig:progenitor_abundances}). Nuclides are categorized
based on the time at which they were maximally abundant in the network
and shaded by their maximum abundance.  Nuclides within the purple
color palette were maximally abundant during the initial
``fuel-burning'' stage after the beginning of fusion and before the
\Si{28} becomes equally abundant with \C{12}, the \C{12}-\Si{28}
crossing time $t_{\rm fa}$.  Blue nuclides were maximally abundant
after $t_{\rm fa}$ but prior to the \Ox{16}-\Si{28} crossing time
$t_{\rm aq}$, and nuclides maximally abundant after $t_{\rm aq}$ but
before the \Si{28}-\Fe{54} crossing time $t_{\rm qn}$ are plotted in
green. Nuclides maximally abundant following $t_{\rm qn}$ are IGEs
together with protons and alpha particles and are shaded in
orange. Note that for the time scales we adopt the notation of
\citep{townetal15}, which describes the burning stages in detail.

The burning model we are using computes the rates for progression
through the burning stages from the local temperature and the energy
release from a set of major fuel abundances, previously including
\C{12}, \Ox{16}, and \Ne{22}. We have found here that any \Ne{20} is
consumed along with \C{12} and that otherwise the burning is quite
similar to that with just \C{12} and \Ox{16} as principal
constituents. In consequence, the only necessary modification to our
burning model is to include \Ne{20} in the abundances of the initial
state in the burning model. This accounts for the difference in
binding energy of \Ne{20} compared to \C{12} and gives lower burning
temperatures. Additionally, throughout the majority of the progenitor
outside the core ignition region, due to prior convective mixing, the
\C{12} content is high enough that we will extrapolate the laminar flame speeds of
\citet{timmes92,Chametal08}. We consider this a reasonable
approximation since much of the flame propagation is dominated by
Rayleigh-Taylor overturn and turbulence.

\subsection{Mapping a \MESA\ Profile to \FLASH\ While Preserving Hydrostatic Equilibrium}
\label{subsec:mesa_flash_mapping}
The temperature and composition at the base of the convective zone in
the hybrid C-O-Ne white dwarf provides a natural flame initialization
region for simulation of thermonuclear runaway in the DDT scenario, so
we map the \MESA\ profile into the \FLASH\ domain preserving its
features at $4$~km spatial resolution. We do this by first converting
the \MESA\ model to a uniform grid by mass-weighted averaging of
quantities in \MESA\ zones with spacing less than $4$~km and using
quadratic interpolation to estimate quantities where \MESA\ zones have
spacing greater than $4$~km. Although our combustion model in
\FLASH\ does not evolve nuclide abundances, it uses the initial
abundances of \C{12}, \Ne{20} and \Ne{22} (assuming the rest is \Ox{16}) to compute the
initial mean nuclear binding energy and electron fraction.
%properties\footnote{The
%  initial abundances determine the following properties of fuel and
%  ash, assuming that \C{12} and \Ne{20} burning produces only \Mg{24}:
%  $Y_e$, $Y_i$, and the average binding energy per baryon
%  $\overline{Q}$} used to evolve the fuel-to-ash progress variable.
Therefore, we also represent the full set of nuclides in the
\MESA\ profile by this reduced set of four nuclides in the uniformly
gridded profile, requiring the carbon mass fractions to be identical
because there is still sufficient \C{12} in the star to sustain a
detonation front. In addition, we use \Ne{22} in the reduced set to
account for the $Y_e$ of the full set of nuclides, and we constrain
\Ne{20} and \Ox{16} to be in the same ratio $R$ in both sets of
abundances. These constraints provide the following definitions for
the reduced abundances used for \FLASH:

%% \begin{subequations}
%% \begin{align}
%% \mathrm{X_{\C{12}}^{FLASH}} &= \mathrm{X_{\C{12}}^{MESA}} \\
%% \mathrm{X_{\Ne{22}}^{FLASH}} &= \mathrm{22 \cdot \left(\dfrac{1}{2}-Y_e^{MESA}\right)} \\
%% \mathrm{R} &= \mathrm{X_{\Ne{20}}^{MESA}/X_{\Ox{16}}^{MESA}} \\
%% \mathrm{X_{\Ox{16}}^{FLASH}} &= \mathrm{\frac{1 - X_{\C{12}}^{FLASH} - X_{\Ne{22}}^{FLASH}}{R + 1}} \\
%% \mathrm{X_{\Ne{20}}^{FLASH}} &= \mathrm{R \cdot X_{\Ox{16}}^{FLASH}}
%% \end{align}
%% \end{subequations}

@@

Nothing constrains the resulting uniformly gridded profile to be in
hydrostatic equilibrium (HSE), however, so we next construct an
equilibrium profile by applying the HSE pressure
constraint
\begin{equation}\label{eq:hse_pressure}
  P_{EOS}(\rho_i,T_i,X_i) = \frac{g \Delta r}{2} (\rho_i +
  \rho_{i-1})\ .
\end{equation}
Starting at the uniformly gridded profile's central density and using
its temperature and composition in each zone together with the HELM
equation of state (EOS) of~\citet{castro1}, we solve
\eqqref{eq:hse_pressure} for the density in each zone. In
\eqqref{eq:hse_pressure}, $\Delta r$ indicates the zone width, $T_i$
is the temperature in zone $i$, $X_i$ is the composition in zone $i$,
and $g$ is the gravitational acceleration at the boundary of zone $i$
and $i-1$ due to the mass enclosed by zone $i-1$ and below. The
resulting uniformly gridded, equilibrium profile (\FLASH) and the
original profile (\MESA) are shown for comparison in Figures
\ref{fig:progenitor_abundances} and \ref{fig:progenitor_temperatures}.
The values of the total mass before and after this procedure differ by
$6 \times 10^{-3}\ \mathrm{M_\odot}$.  This procedure produced a
structure that was stable in \FLASH, with fluctuations in central
density less than $3\%$, for at least $5$ seconds with no energy
deposition. Finally, we replaced the EOS routine in the public
\FLASH\ distribution with that from
\CASTRO\ ~\citep{timmes.swesty:accuracy,castro1} to obtain a more
consistent tabulation.\footnote{The Helmholtz EOS table used in
  \CASTRO\ is in the public BoxLib Microphysics repository at
  \url{https://github.com/BoxLib-Codes/Microphysics.git} (commit hash
  $\mathrm{45ed859b6c1dc80d831d93f9728986d6ad6e1ddc}$).}

%\begin{equation}\label{eq:hse_pressure} P_{EOS}(\rho_i,T_i,X_i)
%= \frac{g \Delta r}{2} (\rho_i + \rho_{i-1}) \end{equation}
%DON: This equation should have dPeos on the left, I'll check it!
%DON: Also, what's the right citation for the HELM EOS? We used the one from Castro, but it's being phased out...
